---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# stocBM
A set of functions to get the partitions of a stochastic blockmodel for
mobility networks; that is, for a cross-classification matrix in which 
rowsums differ between rows AND rowsums and columnsums differ.
In other words, a stochastic blockmodel for directed, weighted networks,
which is conditional on the in- and out-degree distribution.


## Installation

You can install the current version of stocBM from GitHub using:

``` r
# install.packages("remotes")
remotes::install_github("perblock/stocBM")
```

## Small example

First, we create a matrix of counts as an example and add some structure:

``` {r}
library(stocBM)

test_mat <- matrix(rpois(1600, lambda = 10), nrow = 40, ncol = 40)
test_mat[1:15, 1:15] <- test_mat[1:15, 1:15] + 2  # Add some structure
test_mat[25:40, 16:24] <- test_mat[25:40, 16:24] + 3  # Add some structure

# Look at the first rows and columns
test_mat[1:10, 1:10]
```



Now we can run a simple first test to get a (probably) preliminary partitioning. In case the partitions are very clear, this might already
be pretty good.

``` {r}
init_res <- repeat_until_no_improvement(test_mat, n_blocks = 3, max_iter = 1000)
init_res$partition
```

Ok, that looks not ideal, there are some misclassified nodes.
Next, we do a more extensive sampling of different good partitions
and a plot of average same block membership:

```{r}
repeat_result <- repeat_sample_likely_partition(test_mat, n_blocks = 3, n_runs = 10, n_iter = 1000)
repeat_result$partitions

average_partition_matrix(repeat_result)
```

Now that looks better. We can also use this output to optimise the different sampled partitions to find the best (from our current partitioning).

```{r}
get_good_partitions(repeat_result)
```

This tells us how many different solutions are found (fewer = better) and what the best partition is.



