---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# stocBM
A set of functions to get the partitions of a stochastic blockmodel for
mobility networks; that is, for a cross-classification matrix in which 
rowsums differ between rows AND rowsums and columnsums differ.
In other words, a stochastic blockmodel for directed, weighted networks,
which is conditional on the in- and out-degree distribution.


## Installation

You can install the current version of stocBM from GitHub using:

``` r
# install.packages("remotes")
remotes::install_github("perblock/stocBM")
```

## Small example

First, we create a matrix of counts as an example and add some structure:

``` {r}
test_mat <- matrix(rpois(1600, lambda = 10), nrow = 40, ncol = 40)
test_mat[1:15, 1:15] <- test_mat[1:15, 1:15] + 2  # Add some structure
test_mat[25:40, 16:24] <- test_mat[25:40, 16:24] + 5  # Add some structure

# Look at the first rows and columns
test_mat[1:10, 1:10]
```



